%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements (should be included in a modern tex distribution):
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt]{article}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Rahul Dave}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Harvard University}
\def\myaddress{}
\def\myemail{rahuldave@gmail.comu}
\def\myweb{http://rahuldave.nareau.com}
\def\myphone{(267) 257-3027}
%\def\myfax{(919) 660-5623}
\def\myversion{}
\def\myrevision{}



\date{} % not used (revision control instead)
\def\mykeywords{Rahul, Dave Rahul Dave, Vita, CV, Resume, Statistics Machine Learning Applied Computational Science}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
\input{vc}

%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}
%%\usepackage{revnum} % for reverse-numbered publications (revnumerate environment) if needed.

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage[usenames,dvipsnames]{color}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
%\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Minion Pro} 
%\setsansfont[Mapping=tex-text,Colour=AA0000]{Myriad Pro}
%\setmonofont[Mapping=tex-text,Scale=0.9]{Consolas} 


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}

%% git revision control footer 
\rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc, and also remove the \input{vc} line above.

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize \href{http://adslabs.org}{Harvard CfA} \\ 60 Garden St, \\ \vspace{-0.05in} Cambridge, \textsc{ma} 02144}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: \myphone \\ 
  %Fax: \myfax  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}
\end{minipage}


\medskip

%% Name 
\noindent{\Large {\textsc{rahul dave}}}
\reversemarginpar

\medskip       

%% Appointments
\medskip
\marginhead{Goals}


\ind Teaching: To combine computation and science in service of communicating concepts to students by reducing them to their essence. To experiment with innovative techniques from software development and online learning to enhance both the development of both conceptual and implementation skills. 

\ind Research: To develop fast computational techniques for automatic analysis of astronomical objects. To optimize information retrieval for scientists using past searching history, and based on the stage of their career and their specific interests. INFERENCE.


\medskip

\marginhead{Appointments}

\noindent\emph{Harvard University \vspace{0.01in}}

\ind 2013--Present. Educator and TA: Harvard University SEAS and Library

\ind 2010--Present. Computational Scientist: Astrophysical Data Systems (ADS) at the Center for Astrophysics (CfA).      

\ind 2007--2009. Computational Scientist: Initiative in Innovative Computing (IIC).

\medskip

\noindent\emph{University of Pennsylvania \vspace{0.01in}}

\ind 2002--2006. Researcher, Taiwan America Occultation Survey (TAOS).
\ind 1998-2002. Associate Director, Eniac 2000 and Liniac Supercomputing Projects.

\bigskip

%% Education

\marginhead{Education}

\noindent\emph{University of Pennsylvania \vspace{0.01in}}

\ind 2002. Ph.D, Physics.  Dissertation: \emph{Missing energy in the universe: Quintessence and the microwave background}. 
  
\medskip
\noindent\emph{St. Xaviers College, University of Bombay\vspace{0.02in}}

\ind 1993. B.S. Physics ( Honors.) 

\bigskip
 
%% Publications
\marginhead{{\vskip 0.4em}Projects and \newline Presentations}
\medskip 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}
\ind 2005. ``The Political Economy of Presumed Consent.'' University of California, Los Angeles. May.

\ind 2005. ``Last Best Gifts: Altruism and the Market for Human Organs.''
University of California, Berkeley. April.

\ind 2005. ``Cadaveric Organ Procurement and Presumed Consent Laws.'' DePaul
Law Review \& Health Law Institute Symposium on \emph{Precious Commodities: The
Supply and Demand of Body Parts}. Chicago. March. 

\ind 2005. ``Last Best Gifts: Altruism and the Market for Human 
Organs.'' University of Washington. February. 

\ind 2004. ``The Institutional Context of Organ Procurement.'' Indiana
University--Purdue University, Indianapolis. November.

\ind 2004. ``The Political Economy of Presumed Consent.'' \textsc{spt} Program,
Australian National University, \textsc{rsss}. July. 

\ind 2004. ``Organ Procurement in the United States.'' National University of
Ireland at Maynooth. April. 

\ind 2004. ``The Institutional Context of Organ Procurement.'' Indiana
University--Purdue University, Indianapolis. November.

\ind 2004. ``The Political Economy of Presumed Consent.'' \textsc{spt} Program,
Australian National University, \textsc{rsss}. July. 

\ind 2004. ``Organ Procurement in the United States.'' National University of
Ireland at Maynooth. April. 

%\end{revnumerate}
%\newpage
\bigskip

\marginhead{{\vskip 0.3em}Selected \newline Publications}
\medskip
\ind Marion Fourcade and Kieran Healy. 2007. ``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311. 

\ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 

\ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
 \emph{American Sociological Review} 69:~387--404.

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
  Political Philosophy} 10:~478--500. 

\ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
  of Arts Management, Law and Society} 32:~86--103. 


\ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
  Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--\,1657.


\ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of \textsc{hiv} in the U.S. Blood Supply: Organizations,
  Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.


\ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
Recession or Labor Decline?}''  \emph{European Sociological Review}
15:~233--249.


\ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
  social structure}.'' \emph{Sociology} 32:~509--522. 

%\end{revnumerate}

\bigskip

%\newpage

\marginhead{{\vskip 0.4em}Skills \newline (by topic)}
\medskip

\ind Data Science: Machine Learning, Statistics, Numerical Programming, Databases.

\ind Computing: parallel, functional, architecture, scientific, simulation, multi-agent

\ind Programming Languages: python, matlab, R, julia, javascript, coffeescript, scheme/clojure, java, C, C++, fortran

\ind Software: postgresql, redis, mongodb, node.js, flask, django, AWS, MPI, Hadoop, Netlogo, RDF

\ind Architecture: semantic web, large database, web, cluster

\ind Science: Cosmology, Astronomy, Physics, Economics


\bigskip
\marginhead{{\vskip 0.9em}Other}
\medskip

\medskip

\ind Avid Skier, rock climber and hiker

\end{document}
